%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{hyperref}
\usepackage{rotating, graphicx}



\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Jennifer V. Medina}{
\href{mailto:jv.medina42@gmail.com}{jv.medina42@gmail.com} | 786-338-1462 \\
\urlstyle{same}  \href{https://www.linkedin.com/in/jennifer-medina-a53a0332}{LinkedIn}
}




\begin{minipage}[t]{0.9\textwidth} 



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\runsubsection{Florida International University}
\descript{| B.S. in Physics with Minor in Astronomy}
\location{Expected May 2017 | Miami, FL \\ Advisor: Dr. Walter Van Hamme}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERNSHIPS AND WORK EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Internships and Work Experience}

\runsubsection{TAURUS Research Scholar}
\descript{| Jun 2016 - Aug 2016 }
\location{Advisor: Dr. Andrew Mann | University of Texas, Austin, TX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize} \item REU Program for undergraduate students pursuing a career in Astronomy.\item Developed a program in Python to accurately calculate the inclination of host stars in extra-solar planet systems in the Praesepe star cluster. \item Development involved data reduction, modeling, statistical analysis, data interpretation, and collaboration with other scientists. 
\end{tightemize}
\sectionsep

\runsubsection{Telescope Operator}
\descript{| May 2016 - Present }
\location{Supervisor: Dr. James Webb | Stocker Observatory, Miami, FL}
\begin{tightemize}
\item Work involves setting up telescopes and speaking to the public on the topic of astronomy. \item Responsibilities include maintaining the telescopes, taking images with a 24" reflector telescope, and reducing them using the MIRA imaging program. \item Work also involves teaching students how to use and set up a motored reflector telescope, and providing tours of the Observatory.\end{tightemize}
\sectionsep

\runsubsection{Undergraduate Research Assistant}
\descript{| May 2015 - Jun 2016 }
\location{Advisor: Dr. Walter Van Hamme | Florida International University, Miami, FL}
\begin{tightemize}
\item {\it KEPLER} light curves of the HAT-P 7 and HAT-P 11 binary systems were extracted from NASA archives and analyzed with GNUplot using a program developed on UNIX. \item Using this data, parameters and characteristics of the star-planet system were calculated and compared to literature values.\end{tightemize}
\sectionsep

\runsubsection{Learning Assistant: Physics I and II}
\descript{| Aug 2014 - Jan 2017}
\location{Supervisor: Dr. Xuewen Wang | Florida International University, Miami, FL}
\begin{tightemize}
\item Work involved helping students understand fundamental concepts from the lecture through experiments in the laboratory. \item Mentored groups of students and conducted one-on-one teaching. \item Other tasks included setting up equipment and preparing software for the students to use in their data analysis.\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}
\descript{Andrew W. Mann, Eric Gaidos, Andrew Vanderburg, Aaron C. Rizzuto, Megan Ansdell, Jennifer Vanessa Medina, Gregory N. Mace, Adam L. Kraus, Kimberly R. Sokal} (2017) "Zodiacal Exoplanets in Time (ZEIT). IV. Seven transiting planets in the Praesepe cluster" \\ Volume 153, Number 2     \\
Published on: {\it The Astronomical Journal (AJ)}
\\
\location{
\href{http://iopscience.iop.org/article/10.1088/1361-6528/aa5276/meta}{Available Here}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\section{Skills}
\begin{tabular}{ll}
Programming and Software & 

Python, 
\LaTeX, 
HTML, 
Tableu, 
ServiceNow,
Qualtrix,\\
 &

FORTRAN, 
Microsoft Office, 
GNUplot, 
R, 
Matlab \\

OS & 


Windows 
iOS, 
LINUX \\

Technical &

Data Analysis, 
Image Reduction, 
Statistical Interpretation, 
Problem Solving \\

Languages & 
English (Fluent),
Spanish (Fluent),
French (Some)
\end{tabular}






\end{minipage} 

\end{document}